Optimal (Multiway) Spatial Joins

### 2024-05-25 msj.tex
yufei

We now solve a $(k-1)$-SJ problem with $R_1, ..., R_{k-3}, H', V$ as the input using the algorithm $\A$ supplied (see Lemma~\ref{lmm:hv}). This $(k-1)$-SJ has an input size at most $n$, and let us represent its result as $\J(R_1, ..., R_{k-3}, H', V)$. We prove in Appendix~\ref{app:hv}:

@@

The $(k-1)$-SJ can be settled in $F_{k-1}(n, \out)$ time.

>>>>

Now, solve a $(k-1)$-SJ problem with $R_1, ..., R_{k-3}, H', V$ as the input using the algorithm $\A$ supplied (see Lemma~\ref{lmm:hv}). Let $\J(R_1, ...,$ $R_{k-3}, H', V)$ represent the result of this $(k-1)$-SJ. As the $(k-1)$-SJ has an input size at most $n$, given the lemma below (which is proved in Appendix~\ref{app:hv}), we assert that $\J(R_1, ..., R_{k-3}, H', V)$ can be computed in $F_{k-1}(n, \out)$ time.

@@
